---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library("gradethis")
library("learnr")
library("learnrhash")
# library("packrat")
library("tidyverse")
library("visualize")
knitr::opts_chunk$set(echo = FALSE)
```

# Math 32 LearnR Tutorial 3

Today, you are picking an avocado for dinner tonight.  In the bin, suppose that there is a 32 percent chance of randomly selecting a ripe avocado.  If you are picking avocados from the bin, you keep inspecting avocados and stop upon finding a ripe avocado.  If you buy a bag of avocados, you do not inspect the fruit until you get home and inspect the bag of avocados all at once.  For this math assignment, assume that either the binomial or geometric distribution is the best model for the situation.

## Bin(n,p) or Geo(p)

For the following calculations, use the `dbinom`, `pbinom`, `dgeom`, or `pgeom` commands (maybe along with other R functions that have been introduced).

### Exactly

What is the probability that you inspect exactly 2 avocados from the bin?

```{r q1, exercise = TRUE, exercise.lines = 1}

```

```{r q1-check}
grade_this({
  if (abs(.result - dgeom(1, 0.32) ) < 0.001){
    pass()
  }
  fail()
})
```

What is the probability that you have exactly 3 ripe avocados in a bag of 7 avocados?

```{r q2, exercise = TRUE, exercise.lines = 1}

```

```{r q2-check}
grade_this({
  if (abs(.result - dbinom(3, 7, 0.32) ) < 0.001){
    pass()
  }
  fail()
})
```


### Fewer

What is the probability that you have fewer than 4 ripe avocados among a bag of 8 avocados?

```{r q3, exercise = TRUE, exercise.lines = 1}

```

```{r q3-check}
grade_this({
  if (abs(.result - sum(dbinom(0:4, 8, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

What is the probability that you inspect fewer than 5 avocados from the bin?

```{r q4, exercise = TRUE, exercise.lines = 1}

```

```{r q4-check}
grade_this({
  if (abs(.result - sum(dgeom(0:3, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

### More

What is the probability that you inspect more than 2 avocados from the bin?

```{r q5, exercise = TRUE, exercise.lines = 1}

```

```{r q5-check}
grade_this({
  if (abs(.result - (1 - sum(dgeom(0:1, 0.32))) ) < 0.001){
    pass()
  }
  fail()
})
```

What is the probability that you have more than 3 ripe avocados in your bag of 6 avocados?

```{r q6, exercise = TRUE, exercise.lines = 1}

```

```{r q6-check}
grade_this({
  if (abs(.result - sum(dbinom(4:6, 6, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```


## Inclusive Inequalities

In mathematics, the *strict* inequalities are "less than" ($<$) and "greater than" ($>$); while the *inclusive* inequalities are "less than or equal" ($\leq$) and "greater than or equal" ($\geq$).

### At Least

What is the probability that you have at least 4 ripe avocados in your bag of 7 avocados?

```{r q7, exercise = TRUE, exercise.lines = 1}

```

```{r q7-check}
grade_this({
  if (abs(.result - sum(dbinom(4:7, 7, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

What is the probability that you inspect at least 1 avocado from the bin?

```{r q8, exercise = TRUE, exercise.lines = 1}

```

```{r q8-check}
grade_this({
  if (abs(.result - (1 - dgeom(0, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

### At Most

What is the probability that you inspect at most 4 avocados from the bin?

```{r q9, exercise = TRUE, exercise.lines = 1}

```

```{r q9-check}
grade_this({
  if (abs(.result - sum(dgeom(0:3, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

What is the probability that you have at most 5 ripe avocados from the your bag of 9 avocados?

```{r q10, exercise = TRUE, exercise.lines = 1}

```

```{r q10-check}
grade_this({
  if (abs(.result - sum(dbinom(0:5, 9, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

## Visualize

Here are some examples of using the `visualize` package (created by Dr. Balamuta at UIUC)

```{r binom-at-most, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, size = 5, prob = 0.32, section = "lower", strict = FALSE)
```

```{r binom-more, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, size = 5, prob = 0.32, section = "upper", strict = TRUE)
```

```{r geom-less, exercise = TRUE, exercise.lines = 2}
visualize.geom(stat = 3, prob = 0.32, section = "lower", strict = TRUE)
```

```{r geom-at-least, exercise = TRUE, exercise.lines = 2}
visualize.geom(stat = 3, prob = 0.32, section = "upper", strict = FALSE)
```

## Binomial CMF

On this page, $X \sim \text{Bin}(6, 0.32)$

Use the `visualize.binom` function to create the graph of $P(k < 4)$

```{r q11, exercise = TRUE, exercise.lines = 2}

```

```{r q11-solution}
visualize.binom(stat = 4, size = 6, prob = 0.32, section = "lower", strict = TRUE)
```

```{r q11-check}
grade_this_code()
```

Use the `visualize.binom` function to create the graph of $P(k \geq 2)$

```{r q12, exercise = TRUE, exercise.lines = 2}

```

```{r q12-solution}
visualize.binom(stat = 2, size = 6, prob = 0.32, section = "upper", strict = FALSE)
```

```{r q12-check}
grade_this_code()
```


## Geometric CMF

On this page, $X \sim \text{Geom}(0.32)$

Use the `visualize.geom` function to create the graph of $P(k > 3)$

```{r q13, exercise = TRUE, exercise.lines = 2}

```

```{r q13-solution}
visualize.geom(stat = 3, prob = 0.32, section = "upper", strict = TRUE)
```

```{r q13-check}
grade_this_code()
```

Use the `visualize.geom` function to create the graph of $P(k \leq 4)$

```{r q14, exercise = TRUE, exercise.lines = 2}

```

```{r q14-solution}
visualize.geom(stat = 4, prob = 0.32, section = "lower", strict = FALSE)
```

```{r q14-check}
grade_this_code()
```


## Concept Checks

```{r q15}
question("The geometric distribution has the memoryless property",
  answer("TRUE", correct = TRUE),
  answer("FALSE"),
  allow_retry = TRUE
)
```

```{r q16}
question("The geometric distribution is the only discrete distribution that has the memoryless property",
  answer("TRUE", correct = TRUE),
  answer("FALSE"),
  allow_retry = TRUE
)
```



## Wrap Up

Type your name and UC Merced e-mail address inside the quotation marks

```{r student-info, exercise = TRUE}
student_name  <- ""
student_email <- ""
```


```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(
  ui_before = default_ui(url = "https://catcourses.ucmerced.edu")
)
```


